\documentclass[margin,line]{res}
\usepackage{hyperref}

\oddsidemargin -.5in
\evensidemargin -.5in
\textwidth=6.0in
\itemsep=0in
\parsep=0in
\parskip=0.15in

\newcommand{\dated}[2]{\parbox[t]{4.4in}{#1} \hspace{0.4in}
											 \parbox[t]{1in}{ {\it #2 } } }

\begin{document}

\name{John DeNero \vspace*{.1in}}

\begin{resume}

\section{\sc Contact Information}
\vspace{.05in}
\begin{tabular}{@{}p{2in}lp{4in}}
781 Soda Hall         & {\it Phone:} & (415) 203-1943        \\
UC Berkeley           & {\it Email:} & denero@berkeley.edu   \\
Berkeley, CA  94720   & {\it Web:}   & http://www.denero.org \\
\end{tabular}

\section{\sc Positions}

	\dated{Assistant Teaching Professor, UC Berkeley, in Computer Science}
	{ 2014-present } \\

	\dated{Senior Research Scientist, Google Inc., in Google Translate}
	{ 2010-2014 } \\

\section{\sc Education}

	{\bf University of California, Berkeley} \\
	\dated{Ph.D., Computer Science \\
	\hspace*{1em} {\it Advisor}: Dan Klein}{ 2005-2010 }

	{\bf Stanford University} \\
	\dated{Master of Arts, Philosophy\vspace{0.12in}}{ 2001-2002 } \\
	\dated{Bachelor of Science, with distinction \\
	\hspace*{1em} {\it Major}: Mathematical and Computational Science \\
	\hspace*{1em} {\it Secondary Major}: Symbolic Systems}{ 1998-2002 }

\section{\sc Awards}

\dated{Giancarlo Teaching Fellow, College of Engineering} { 2017 }

\dated{Jim and Donna Gray Award for Excellence in Undergraduate Teaching, EECS Department} { 2017 }

\dated{Diane McEntyre Award for Excellence in Teaching, EECS Department} { 2016 }

\dated{Award for Excellence in Promoting Women in Undergraduate Computing, Honorable Mention, NCWIT} { 2016 }

\dated{Voted Best Faculty Member on Campus, Daily Cal} { 2016 }

\dated{Outstanding Faculty of the Year Award, Tau Beta Pi} { 2015 }

\section{\sc Selected Publications}

\small

Joern Wuebker, Spence Green, John DeNero, Sasa Hasa, and Thang Luong. `` Models and Inference for Prefix-Constrained Machine Translation,'' in {\it Proceedings of the Association of Computational Linguistics}, 2016.

Joern Wuebker, Spence Green, and John DeNero. ``Hierarchical Incremental Adaptation for Statistical Machine Translation,'' in {\it Proceedings of Empirical Methods in Natural Language Processing}, 2015.

Rohan Chitnis and John DeNero. ``Variable-Length Word Encodings for Neural Translation Models,'' in {\it Proceedings of Empirical Methods in Natural Language Processing}, 2015.

Karl Pichotta and John DeNero.  ``Identifying Phrasal Verbs Using Many Bilingual Corpora,'' in {\it Proceedings of the Conference on Empirical Methods in Natural Language Processing}, 2013.

Greg Durrett and John DeNero.  ``Supervised Learning of Complete Morphological Paradigms,'' in {\it Proceedings of the North American Association of Computational Linguistics}, 2013.

David Golland, John DeNero, and Jakob Uszkoreit. ``A Feature-Rich Constituent Context Model for Grammar Induction,'' in {\it Proceedings of the Association of Computational Linguistics}, 2012.

Spence Green and John DeNero. ``A Class-Based Agreement Model for Generating Accurately Inflected Translations,'' in {\it Proceedings of the Association of Computational Linguistics}, 2012.

Mohit Bansal, John DeNero, and Dekang Lin. ``Unsupervised Translation Sense Clustering,'' in {\it Proceedings of the North American Association of Computational Linguistics}, 2012.

John DeNero and Jakob Uszkoreit.  ``Inducing Sentence Structure from Parallel Corpora for Reordering,'' in {\it Proceedings of the Conference on Empirical Methods in Natural Language Processing}, 2011.

John DeNero and Klaus Machery. ``Model-Based Aligner Combination Using Dual Decomposition,'' in {\it Proceedings of the Association of Computational Linguistics}, 2011.

John DeNero and Dan Klein. ``Discriminative Modeling of Extraction Sets for Machine Translation,'' in {\it Proceedings of the Association of Computational Linguistics}, 2010.

John DeNero, Shankar Kumar, Ciprian Chelba, and Franz Och. ``Model Combination for Machine Translation,'' in {\it Proceedings of the North American Association of Computational Linguistics}, 2010.

Taylor Berg-Kirkpatrick, Alexandre Bouchard-Côté, John DeNero, and Dan Klein. ``Painless Unsupervised Learning with Features,'' in {\it Proceedings of the North American Association of Computational Linguistics}, 2010.

John DeNero, David Chiang, and Kevin Knight. ``Fast Consensus Decoding over Translation Forests,'' in {\it Proceedings of the Association of Computational Linguistics}, 2009.

Adam Pauls, John DeNero, and Dan Klein. ``Consensus Training for Consensus Decoding in Machine Translation,'' in {\it Proceedings of the Conference on Empirical Methods in Natural Language Processing}, 2009.

John DeNero, Adam Pauls, and Dan Klein. ``Asynchronous Binarization for Synchronous Grammars,'' in {\it Proceedings of the Association of Computational Linguistics, Short Paper Track}, 2009.

John DeNero, Mohit Bansal, Adam Pauls, and Dan Klein. ``Efficient Parsing for Transducer Grammars,'' in {\it Proceedings of the North American Association of Computational Linguistics}, 2009.

John DeNero, Alex Bouchard-Côté, and Dan Klein. ``Sampling Alignment Structure under a Bayesian Translation Model,'' in {\it Proceedings of the Conference on Empirical Methods in Natural Language Processing}, 2008.

John DeNero and Dan Klein. ``The Complexity of Phrase Alignment Models,'' in {\it Proceedings of the Association of Computational Linguistics, Short Paper Track}, 2008.

John DeNero and Dan Klein. ``Tailoring Word Alignments to Syntactic Machine Translation,'' in {\it Proceedings of the Association of Computational Linguistics}, 2007.

John DeNero, Dan Gillick, James Zhang, and Dan Klein. ``Why Generative Phrase Models Underperform Surface Heuristics,'' in {\it Proceedings of the Workshop on Statistical MT}, 2006.

\section{\sc Activities}

{\bf Organizing Committee}: EAAI '13, EAAI '14, NACLO/ELCLO '13, NACLO/ELCLO '14,
EMNLP '15 (Session chair), NAACL '16 (Demonstration chair), EMNLP '16 (Area chair)

{\bf Conference Reviewer}: EMNLP '08, NAACL '09, ACL '09, EMNLP '09, MT Summit
'09,\\ NAACL '10, ACL '10, COLING '10, ACL '11, AAAI '11, EMNLP '11, NAACL '12,
ACL '12, EMNLP '12, EAAI '12, NAACL '13, ACL '13, EMNLP '13, EACL '14,
NAACL '15, ACL '15, EMNLP '15

\end{resume}
\end{document}
